Model Comparisons

### 2015-11-28 models/Model_Comparison.Rmd
tweaks to performance storage

    # MSE
    return(mean((md$pred - md$listener.p)^2))
  })  
  # get lowest MSE
  best.alpha = which(fit == min(fit))
  return(best.alpha)
}
```

@@

### Data for entailment models
```{r entailment_models_data, message=FALSE, warning=FALSE}
speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
# Uniform priors
priors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
# Combine speaker / listener
data.partial = left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
```

@@

# Model 1 - Entailment only models
# --------------------------------
# 1.a)
# Entailment only
# Normalized = T
# alpha tuning = F
alphas[1] = 1
m1.a = data.partial %>%
  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=T))
# Store output
performance.output[1, ] = c("m1.a", round(cor(m1.a$listener.p, m1.a$pred), 5), T)
# Store plot
m1.a.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m1.a,
      main=paste("m1.a\nalpha: ", alphas[1], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.b)
# Entailment only
# Normalized = F
# alpha tune = F
alphas[2] = 1
m1.b = data.partial %>%
  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=F))
# Store output
performance.output[2, ] = c("m1.b", round(cor(m1.b$listener.p, m1.b$pred), 5), F)
# Store plot
m1.b.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m1.b,
      main=paste("m1.b\nalpha: ", alphas[2], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.c)
# Entailment only
# Normalized = T
# alpha tune = T
alphas[3] = tune.alpha(data.partial, normalize=T)
m1.c = data.partial %>%
  do(run.partial(., alpha = alphas[3], useprior=T, usenone=F, normalize=T))
# Store output
performance.output[3, ] = c("m1.c", round(cor(m1.c$listener.p, m1.c$pred), 5), normalized=T)
# Store plot
m1.c.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m1.c,
      main=paste("m1.c\nalpha: ", alphas[3], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.d)
# Entailment only
# Normalized = F
# alpha tune = T
alphas[4] = tune.alpha(data.partial, normalize=F)
m1.d = data.partial %>%
  do(run.partial(., alpha = alphas[4], useprior=T, usenone=F, normalize=F))
# Store output
performance.output[4, ] = c("m1.d", round(cor(m1.d$listener.p, m1.d$pred), 5), normalized=F)
# Store plot
m1.d.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m1.d,
      main=paste("m1.d\nalpha: ", alphas[4], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# Model 2 - Entailment + generic none
# --------------------------------
# 2.a)
# Entailment + generic None
# Normalized = T
# alpha tuning = F
alphas[5] = 1
m2.a = data.partial %>%
  do(run.partial(., alpha = alphas[5], useprior=T, usenone=T, normalize=T))
# Store output
performance.output[5, ] = c("m2.a", round(cor(m2.a$listener.p, m2.a$pred), 5), T)
# Store plot
m2.a.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m2.a,
      main=paste("m2.a\nalpha: ", alphas[5], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.b)
# Entailment + generic None
# Normalized = F
# alpha tune = F
alphas[6] = 1
m2.b = data.partial %>%
  do(run.partial(., alpha = alphas[1], useprior=T, usenone=T, normalize=F))
# Store output
performance.output[6, ] = c("m2.b", round(cor(m2.b$listener.p, m2.b$pred), 5), F)
# Store plot
m2.b.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m2.b,
      main=paste("m2.b\nalpha: ", alphas[6], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.c)
# Entailment + generic None
# Normalized = T
# alpha tune = T
alphas[7] = tune.alpha(data.partial, normalize=T)
m2.c = data.partial %>%
  do(run.partial(., alpha = alphas[7], useprior=T, usenone=T, normalize=T))
# Store output
performance.output[7, ] = c("m2.c", round(cor(m2.c$listener.p, m2.c$pred), 5), normalized=T)
# Store plot
m2.c.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m2.c,
      main=paste("m2.c\nalpha: ", alphas[3], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.d)
# Entailment + generic None
# Normalized = F
# alpha tune = T
alphas[8] = tune.alpha(data.partial, normalize=F)
m2.d = data.partial %>%
  do(run.partial(., alpha = alphas[8], useprior=T, usenone=T, normalize=F))
# Store output
performance.output[8, ] = c("m2.d", round(cor(m2.d$listener.p, m2.d$pred), 5), normalized=F)
# Store plot
m2.d.plot = qplot(stars, e6.listener.p, col=degree, 
      data=m2.d,
      main=paste("m2.d\nalpha: ", alphas[8], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

@@

# Model 3 - Full, alpha tuning
# ----------------------------
alphas[6] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
m3.fit = data.full %>%
  do(run.full(., alpha = alphas[6]))
m3.fit.matched = m3.fit[matched.items, ]
m3.fit.matched$degree = ifelse(m3.fit.matched$degree == "hi1", "hi", "low")
m3.fit.matched = cbind(m3.fit.matched, data.partial$listener.p)
# Check that everything lines up between partial and full
all(m3.fit.matched$scale == data.partial$scale & m3.fit.matched$degree == data.partial$degree)
colnames(m3.fit.matched)[length(colnames(m3.fit.matched))] = "e6.listener.p"
performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred), 5))

# Model 4 - Full, no alpha tuning
# -------------------------------
alphas[7] = 1
m4.noFit = data.full.extras %>%
  do(run.full(., alpha = alphas[7], addMid=T, normalize=T))
m4.noFit.matched = m4.noFit[matched.items.extras, ]
# Need to fix this to dealt with 'mid'
m4.noFit.matched$degree = ifelse(m4.noFit.matched$degree == "hi1", "hi", "low")
m4.noFit.matched = cbind(m4.noFit.matched, data.partial$listener.p)
# Check that everything lines up between partial and full
all(m4.noFit.matched$scale == data.partial$scale & m4.noFit.matched$degree == data.partial$degree)
colnames(m4.noFit.matched)[length(colnames(m4.noFit.matched))] = "e6.listener.p"
# store corr
performance.output[7, ] = c("M4_noFit", round(cor(m4.noFit.matched$e6.listener.p, m4.noFit.matched$pred), 5))

# Model 4 - Full, alpha tuning, added 'mid'
# ----------------------------
alphas[8] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T)
m4.fit = data.full.extras %>%
  do(run.full(., alpha = alphas[8], addMid=T))
m4.fit.matched = m4.fit[matched.items.extras, ]
m4.fit.matched$degree = ifelse(m4.fit.matched$degree == "hi1", "hi", "low")
m4.fit.matched = cbind(m4.fit.matched, data.partial$listener.p)
# Check that everything lines up between partial and full
all(m4.fit.matched$scale == data.partial$scale & m4.fit.matched$degree == data.partial$degree)
colnames(m4.fit.matched)[length(colnames(m4.fit.matched))] = "e6.listener.p"
# store corr
performance.output[8, ] = c("M4_fit", round(cor(m4.fit.matched$e6.listener.p, m4.fit.matched$pred), 5))
```

@@

Overall model performance: $r^2$. M1 and M2 use literal listener values from exp8. M2 includes a generic "None" defined in terms of stars (1: 1.0, 2:0.0, 3:0.0, 4:0.0, 5:0.0). M3 uses the full set of literal listener alternatives from exp10, however r^2 values and tuning reflects comparisons to exp6 pragmatic listener judgments (not exp11).
```{r overall_perf}
performance.output$model = factor(performance.output$model, levels=c(
  "M1_noFit", "M1_fit", "M2_noFit", "M2_fit", "M3_noFit", "M3_fit", "M4_noFit", "M4_fit"
))
# Populate extra model info
performance.output$cor = as.numeric(performance.output$cor)
performance.output$alphas = alphas
performance.output$alts = c(rep("entailment only", 2), rep("entailment + None", 2), rep("full", 2), rep("full + extras", 2))
grid.table(performance.output)

qplot(data=performance.output, x=model, y=performance.output$cor,
      geom="bar", stat="identity",
      main = "Model performance", ylab="r^2", xlab="model") +
  geom_text(aes(label = round(cor, 3), y = cor + 0.02), size = 3) +
  scale_y_continuous(limits=c(0, 1))
```

## Individual model performance
```{r individual_plots}
m1.noFit.G = qplot(stars, listener.p, col=degree, 
      data=m1.noFit,
      main=paste("M1, no fit\nalpha: ", alphas[1]),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
m1.noFit.G

m1.fit.G = qplot(stars, listener.p, col=degree, 
      data=m1.fit,
      main=paste("M1, fit\nalpha: ", alphas[2]),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
m1.fit.G

m2.noFit.G = qplot(stars, listener.p, col=degree, 
      data=m2.noFit,
      main=paste("M2, no fit\nalpha: ", alphas[3]),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
m2.noFit.G

m2.fit.G = qplot(stars, listener.p, col=degree, 
      data=m2.fit,
      main=paste("M2, fit\nalpha: ", alphas[4]),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
m2.fit.G

m3.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
      data=m3.noFit.matched,
      main=paste("M3, no fit\nalpha: ", alphas[5]),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
m3.matched.noFit.G
cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred)

m3.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
      data=m3.fit.matched,
      main=paste("M3, fit\nalpha: ", alphas[6]),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
m3.matched.fit.G
cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)

# Full model fitted - color scale
m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
  geom_point(aes(colour = scale)) +
  geom_smooth(method=lm) +
  ggtitle("Model performance: M3 fit") +
  labs(x = "human judgments", y="model prediction")
m3.matched.fit.CorPlot

# Full model fitted - color stars
m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
  geom_point(aes(colour = stars)) +
  geom_smooth(method=lm) +
  ggtitle("Model performance: M3 fit") +
  labs(x = "human judgments", y="model prediction")
m3.matched.fit.CorPlot

m4.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
      data=m4.noFit.matched,
      main=paste("M4, no fit\nalpha: ", alphas[7]),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
m4.matched.noFit.G

m4.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
      data=m4.fit.matched,
      main=paste("M4, fit\nalpha: ", alphas[8]),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
m4.matched.fit.G
```

# Other exploration
```{r}
bad.predictions = m3.fit.matched$pred > 0 &
                  m3.fit.matched$e6.listener.p == 0 &
                  (m3.fit.matched$pred - m3.fit.matched$e6.listener.p > 0.05)
```

>>>>

    # MSE
    return(mean((md$pred - md$listener.p)^2))
  })  
  # get lowest MSE
  best.alpha = which(fit == min(fit))
  return(best.alpha)
}

# Uniform priors
unif.priors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
emp.priors = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/emp_priors.csv")
priors = unif.priors
```

@@

### Data for entailment models
```{r entailment_models_data, message=FALSE, warning=FALSE}
speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
# Combine speaker / listener
data.partial = left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
```

@@

# Model 1 - Entailment only models
# --------------------------------
# 1.a)
# Entailment only
# Normalized = T
# alpha tuning = F
alphas[1] = 1
m1.a = data.partial %>%
  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=T))
# Store output
performance.output[1, ] = c("m1.a", round(cor(m1.a$listener.p, m1.a$pred), 5), T)
# Store plot
m1.a.plot = qplot(stars, listener.p, col=degree, 
      data=m1.a,
      main=paste("m1.a\nalpha: ", alphas[1], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.b)
# Entailment only
# Normalized = F
# alpha tune = F
alphas[2] = 1
m1.b = data.partial %>%
  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=F))
# Store output
performance.output[2, ] = c("m1.b", round(cor(m1.b$listener.p, m1.b$pred), 5), F)
# Store plot
m1.b.plot = qplot(stars, listener.p, col=degree, 
      data=m1.b,
      main=paste("m1.b\nalpha: ", alphas[2], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.c)
# Entailment only
# Normalized = T
# alpha tune = T
alphas[3] = tune.alpha(data.partial, normalize=T)
m1.c = data.partial %>%
  do(run.partial(., alpha = alphas[3], useprior=T, usenone=F, normalize=T))
# Store output
performance.output[3, ] = c("m1.c", round(cor(m1.c$listener.p, m1.c$pred), 5), normalized=T)
# Store plot
m1.c.plot = qplot(stars, listener.p, col=degree, 
      data=m1.c,
      main=paste("m1.c\nalpha: ", alphas[3], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 1.d)
# Entailment only
# Normalized = F
# alpha tune = T
alphas[4] = tune.alpha(data.partial, normalize=F)
m1.d = data.partial %>%
  do(run.partial(., alpha = alphas[4], useprior=T, usenone=F, normalize=F))
# Store output
performance.output[4, ] = c("m1.d", round(cor(m1.d$listener.p, m1.d$pred), 5), normalized=F)
# Store plot
m1.d.plot = qplot(stars, listener.p, col=degree, 
      data=m1.d,
      main=paste("m1.d\nalpha: ", alphas[4], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# Model 2 - Entailment + generic none
# --------------------------------
# 2.a)
# Entailment + generic None
# Normalized = T
# alpha tuning = F
alphas[5] = 1
m2.a = data.partial %>%
  do(run.partial(., alpha = alphas[5], useprior=T, usenone=T, normalize=T))
# Store output
performance.output[5, ] = c("m2.a", round(cor(m2.a$listener.p, m2.a$pred), 5), T)
# Store plot
m2.a.plot = qplot(stars, listener.p, col=degree, 
      data=m2.a,
      main=paste("m2.a\nalpha: ", alphas[5], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.b)
# Entailment + generic None
# Normalized = F
# alpha tune = F
alphas[6] = 1
m2.b = data.partial %>%
  do(run.partial(., alpha = alphas[6], useprior=T, usenone=T, normalize=F))
# Store output
performance.output[6, ] = c("m2.b", round(cor(m2.b$listener.p, m2.b$pred), 5), F)
# Store plot
m2.b.plot = qplot(stars, listener.p, col=degree, 
      data=m2.b,
      main=paste("m2.b\nalpha: ", alphas[6], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.c)
# Entailment + generic None
# Normalized = T
# alpha tune = T
alphas[7] = tune.alpha(data.partial, normalize=T)
m2.c = data.partial %>%
  do(run.partial(., alpha = alphas[7], useprior=T, usenone=T, normalize=T))
# Store output
performance.output[7, ] = c("m2.c", round(cor(m2.c$listener.p, m2.c$pred), 5), normalized=T)
# Store plot
m2.c.plot = qplot(stars, listener.p, col=degree, 
      data=m2.c,
      main=paste("m2.c\nalpha: ", alphas[7], "\nNormalized = ", T),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

# 2.d)
# Entailment + generic None
# Normalized = F
# alpha tune = T
alphas[8] = tune.alpha(data.partial, normalize=F)
m2.d = data.partial %>%
  do(run.partial(., alpha = alphas[8], useprior=T, usenone=T, normalize=F))
# Store output
performance.output[8, ] = c("m2.d", round(cor(m2.d$listener.p, m2.d$pred), 5), normalized=F)
# Store plot
m2.d.plot = qplot(stars, listener.p, col=degree, 
      data=m2.d,
      main=paste("m2.d\nalpha: ", alphas[8], "\nNormalized = ", F),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

@@

# Model 3 - Full, alpha tuning
# ----------------------------
# alphas[6] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
# m3.fit = data.full %>%
#   do(run.full(., alpha = alphas[6]))
# m3.fit.matched = m3.fit[matched.items, ]
# m3.fit.matched$degree = ifelse(m3.fit.matched$degree == "hi1", "hi", "low")
# m3.fit.matched = cbind(m3.fit.matched, data.partial$listener.p)
# # Check that everything lines up between partial and full
# all(m3.fit.matched$scale == data.partial$scale & m3.fit.matched$degree == data.partial$degree)
# colnames(m3.fit.matched)[length(colnames(m3.fit.matched))] = "e6.listener.p"
# performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred), 5))
# 
# # Model 4 - Full, no alpha tuning
# # -------------------------------
# alphas[7] = 1
# m4.noFit = data.full.extras %>%
#   do(run.full(., alpha = alphas[7], addMid=T, normalize=T))
# m4.noFit.matched = m4.noFit[matched.items.extras, ]
# # Need to fix this to dealt with 'mid'
# m4.noFit.matched$degree = ifelse(m4.noFit.matched$degree == "hi1", "hi", "low")
# m4.noFit.matched = cbind(m4.noFit.matched, data.partial$listener.p)
# # Check that everything lines up between partial and full
# all(m4.noFit.matched$scale == data.partial$scale & m4.noFit.matched$degree == data.partial$degree)
# colnames(m4.noFit.matched)[length(colnames(m4.noFit.matched))] = "e6.listener.p"
# # store corr
# performance.output[7, ] = c("M4_noFit", round(cor(m4.noFit.matched$e6.listener.p, m4.noFit.matched$pred), 5))
# 
# # Model 4 - Full, alpha tuning, added 'mid'
# # ----------------------------
# alphas[8] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T)
# m4.fit = data.full.extras %>%
#   do(run.full(., alpha = alphas[8], addMid=T))
# m4.fit.matched = m4.fit[matched.items.extras, ]
# m4.fit.matched$degree = ifelse(m4.fit.matched$degree == "hi1", "hi", "low")
# m4.fit.matched = cbind(m4.fit.matched, data.partial$listener.p)
# # Check that everything lines up between partial and full
# all(m4.fit.matched$scale == data.partial$scale & m4.fit.matched$degree == data.partial$degree)
# colnames(m4.fit.matched)[length(colnames(m4.fit.matched))] = "e6.listener.p"
# # store corr
# performance.output[8, ] = c("M4_fit", round(cor(m4.fit.matched$e6.listener.p, m4.fit.matched$pred), 5))
```

@@

Overall model performance: $r^2$. M1 and M2 use literal listener values from exp8. M2 includes a generic "None" defined in terms of stars (1: 1.0, 2:0.0, 3:0.0, 4:0.0, 5:0.0). M3 uses the full set of literal listener alternatives from exp10, however r^2 values and tuning reflects comparisons to exp6 pragmatic listener judgments (not exp11).
```{r overall_perf}
performance.output = cbind(performance.output, alphas)
grid.table(performance.output)

m1.a.plot
m1.b.plot
m1.c.plot
m1.d.plot

m2.a.plot
m2.b.plot
m2.c.plot
m2.d.plot

m3.a.plot
m3.b.plot
m3.c.plot
m3.d.plot

m4.a.plot
m4.b.plot
m4.c.plot
m4.d.plot
# performance.output$model = factor(performance.output$model, levels=c(
#   "M1_noFit", "M1_fit", "M2_noFit", "M2_fit", "M3_noFit", "M3_fit", "M4_noFit", "M4_fit"
# ))
# # Populate extra model info
# performance.output$cor = as.numeric(performance.output$cor)
# performance.output$alphas = alphas
# performance.output$alts = c(rep("entailment only", 2), rep("entailment + None", 2), rep("full", 2), rep("full + extras", 2))
# grid.table(performance.output)
# 
# qplot(data=performance.output, x=model, y=performance.output$cor,
#       geom="bar", stat="identity",
#       main = "Model performance", ylab="r^2", xlab="model") +
#   geom_text(aes(label = round(cor, 3), y = cor + 0.02), size = 3) +
#   scale_y_continuous(limits=c(0, 1))
```

## Individual model performance
```{r individual_plots}
# m1.noFit.G = qplot(stars, listener.p, col=degree, 
#       data=m1.noFit,
#       main=paste("M1, no fit\nalpha: ", alphas[1]),
#       ylab="Posterior p(rating | word)") + 
#   facet_wrap(~scale) + 
#   geom_line(aes(y = pred), lty = 4)
# # m1.noFit.G
# 
# m1.fit.G = qplot(stars, listener.p, col=degree, 
#       data=m1.fit,
#       main=paste("M1, fit\nalpha: ", alphas[2]),
#       ylab="Posterior p(rating | word)") + 
#   facet_wrap(~scale) + 
#   geom_line(aes(y = pred), lty = 4)
# m1.fit.G
# 
# m2.noFit.G = qplot(stars, listener.p, col=degree, 
#       data=m2.noFit,
#       main=paste("M2, no fit\nalpha: ", alphas[3]),
#       ylab="Posterior p(rating | word)") + 
#   facet_wrap(~scale) + 
#   geom_line(aes(y = pred), lty = 4)
# m2.noFit.G
# 
# m2.fit.G = qplot(stars, listener.p, col=degree, 
#       data=m2.fit,
#       main=paste("M2, fit\nalpha: ", alphas[4]),
#       ylab="Posterior p(rating | word)") + 
#   facet_wrap(~scale) + 
#   geom_line(aes(y = pred), lty = 4)
# m2.fit.G
# 
# m3.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
#       data=m3.noFit.matched,
#       main=paste("M3, no fit\nalpha: ", alphas[5]),
#       ylab="Posterior p(rating | word)") + 
#   facet_wrap(~scale) + 
#   geom_line(aes(y = pred), lty = 4)
# m3.matched.noFit.G
# cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred)
# 
# m3.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
#       data=m3.fit.matched,
#       main=paste("M3, fit\nalpha: ", alphas[6]),
#       ylab="Posterior p(rating | word)") + 
#   facet_wrap(~scale) + 
#   geom_line(aes(y = pred), lty = 4)
# m3.matched.fit.G
# cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)
# 
# # Full model fitted - color scale
# m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
#   geom_point(aes(colour = scale)) +
#   geom_smooth(method=lm) +
#   ggtitle("Model performance: M3 fit") +
#   labs(x = "human judgments", y="model prediction")
# m3.matched.fit.CorPlot
# 
# # Full model fitted - color stars
# m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
#   geom_point(aes(colour = stars)) +
#   geom_smooth(method=lm) +
#   ggtitle("Model performance: M3 fit") +
#   labs(x = "human judgments", y="model prediction")
# m3.matched.fit.CorPlot
# 
# m4.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
#       data=m4.noFit.matched,
#       main=paste("M4, no fit\nalpha: ", alphas[7]),
#       ylab="Posterior p(rating | word)") + 
#   facet_wrap(~scale) + 
#   geom_line(aes(y = pred), lty = 4)
# m4.matched.noFit.G
# 
# m4.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
#       data=m4.fit.matched,
#       main=paste("M4, fit\nalpha: ", alphas[8]),
#       ylab="Posterior p(rating | word)") + 
#   facet_wrap(~scale) + 
#   geom_line(aes(y = pred), lty = 4)
# m4.matched.fit.G
```

# Other exploration
```{r}
# bad.predictions = m3.fit.matched$pred > 0 &
#                   m3.fit.matched$e6.listener.p == 0 &
#                   (m3.fit.matched$pred - m3.fit.matched$e6.listener.p > 0.05)
```
